Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-05-09 article.rnw
Move the colour definitions within the rnw file.
This means the same colours can be used for coclassification matrices
throughout the document, when new coclassisification matrices are added.
Add a figure showing the alpha values of the "best" model.

@@

The ``best'' model, as indicated by {\ic}, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.

@@

@@

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\colorlet{coclassification diagonal}{black!20}
\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				weighted_col_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive effects (columns of the interaction matrix).}
		\label{fig:coclassification-cols}
	\end{subfigure}

>>>>

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\colorlet{coclassification diagonal}{black!20}

@@

The ``best'' model, as indicated by {\ic}, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
\Cref{fig:best-model} shows the groupings and alpha values of this ``best'' model.
The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.

@@

\begin{figure}
	\centering

	<<echo=FALSE>>=
		best_model_index <- which.max(brute_data$statistics[[ic_weight]])
		best_row_grouping <- brute_data$get_row_grouping(best_model_index)
		best_col_grouping <- brute_data$get_col_grouping(best_model_index)
		best_alpha_matrix <- brute_data$parameters[[best_model_index]]$alpha_values

		ordering <- get_ordering(list(best_row_grouping, best_col_grouping))
		best_species_names <- brute_data$species_names[ordering]
		best_row_grouping <- best_row_grouping[ordering]
		best_col_grouping <- best_col_grouping[ordering]
		best_alpha_matrix <- best_alpha_matrix[ordering,ordering]

		best_row_coclassification <- as_coclassification_matrix(best_row_grouping)
		best_col_coclassification <- as_coclassification_matrix(best_col_grouping)
	@

	\begin{subfigure}{\textwidth}
		\centering
		<<echo=FALSE>>=
			grouped_alpha_matrix(
				best_species_names,
				best_row_grouping,
				best_col_grouping,
				best_alpha_matrix
			)
		@
		\caption{The grouped alpha matrix.}
		\label{fig:best-alpha-matrix}
	\end{subfigure}

	\begin{subfigure}{0.49\textwidth}
		\centering
		<<echo=FALSE>>=
			minimal_coclassification_kable(
				best_col_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{The coclassification matrix of rows.}
		\label{fig:best-coclassification-cols}
	\end{subfigure}
	%
	\begin{subfigure}{0.49\textwidth}
		\centering
		<<echo=FALSE>>=
			minimal_coclassification_kable(
				best_row_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{The coclassification matrix of columns.}
		\label{fig:best-coclassification-rows}
	\end{subfigure}

	\caption{%
		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}). %TODO: Debug this.
		\Cref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.
		\Cref{fig:best-coclassification-cols} and \cref{fig:best-coclassification-rows} show the coclassification matrices derived from the groupings of the columns and rows respectively.
		These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
		Species have been reordered that species which are grouped together appear adjacent.
		The ordering is the same in \cref{fig:best-coclassification-cols} and \cref{fig:best-coclassification-rows} as shown in \cref{fig:best-alpha-matrix}.
	}
	\label{fig:best-model}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				weighted_col_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive effects (columns of the interaction matrix).}
		\label{fig:coclassification-cols}
	\end{subfigure}
